---
title: "Air pollution in China"
author: "Myrsine Lachanaris"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(plotly)
pollution <- read_csv("data/air_pollution_china.csv")
```

# Questions:

## Which city gets the most CO pollution in the summer?

### Descriptive analysis

```{r}
summer <- pollution |>
  filter(Season == "Summer")
summer |>
  ggplot(aes(x = `City`, y = `CO (mg/m³)`)) +
  geom_boxplot()
```

```{r}
summer |>
  group_by(City) |>
  summarize(mean = mean(`CO (mg/m³)`), sd = sd(`CO (mg/m³)`),
            min = min(`CO (mg/m³)`), max = max(`CO (mg/m³)`))
```

### Inferential statistics

```{r}
anova <- aov(`CO (mg/m³)` ~ City, data = summer)
summary(anova)
```

The p-value is greater than 0.05, which means that there is no significant difference in CO levels among the cities.

## What are the effects of CO on temperature in the winter?

### Descriptive analysis

```{r}
winter <- pollution |>
  filter(Season == "Winter")
b <- winter |>
  ggplot(aes(y = `Temperature (°C)`, x = `CO (mg/m³)`)) +
  geom_point(alpha = 0.5)
ggplotly(b)
```

```{r}
winter |>
  summarize(mean = mean(`CO (mg/m³)`), sd = sd(`CO (mg/m³)`),
            min = min(`CO (mg/m³)`), max = max(`CO (mg/m³)`))
winter |>
  summarize(mean = mean(`Temperature (°C)`), sd = sd(`Temperature (°C)`), 
            min = min(`Temperature (°C)`), max = max(`Temperature (°C)`))
```

### Inferential statistics

```{r}
cor.test(winter$`Temperature (°C)`, winter$`CO (mg/m³)`)
```

H\^0: There is no correlation between temperature and CO levels.

H\^1: There is correlation between temperature and CO levels.

Since the p-value is higher than 0.05, we cannot reject the null hypothesis. Therefore, we can determine that there is no correlation between temperature and CO levels in the winter.

## Conclusion

I used a box plot for the first question to compare the CO levels between the cities during the summer. I then used ANOVA to further see if there are any significant differences in CO levels between the cities, which there are none.

I used a scatter plot for the second question to plot CO levels vs temperature in the winter among all cities. I then calculated the correlation between CO levels and temperature, which resulted in no correlation. This proved the graph.
